Simulating Dwarf Galaxy Evolution with Individual Star Feedback and Chemical Evolution

### 2018-02-08 main.tex
Update on Overleaf.

\begin{abstract}
We have developed a new model for stellar feedback in order to simulate the chemodynamical evolution of isolated dwarf galaxies at high resolution in the adaptive mesh refinement code \textsc{Enzo}. For the first time in galaxy scale simulations, we are capable of capturing detailed stellar feedback from individual stars including stellar winds from massive stars and AGB stars, photoelectric heating, Lyman-Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type 1a supernovae. 
%This star-by-star method allows us to directly account for variations in stellar properties that govern their feedback properties (mass, lifetime, surface temperature, and metallicity).
In addition, we follow the evolution of star-by-star stellar yields for 15 metal tracer species \textbf{list here?}. We describe these methods in detail, including the additional physics used to model a realistic three-phase interstellar medium. We present the first application of these methods on a 500~Myr simulation of an isolated dwarf galaxy with properties similar to a Local Group ultrafaint dwarf galaxy. Our methods are capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship. Effective feedback drives significant metal enriched outflows, leading to a low metal retention fractions consistent with observations. Our low-dust content galaxy exhibits a significant H$_2$ mass fraction, formed primarily through gas-phase H$^{-}$ reactions. We end with a discussion on how this work will impact our understanding of galactic chemical evolution on a species-by-species basis.
\end{abstract}

@@

We use the adaptive mesh refinement (AMR) hydrodynamics and N-body code \texttt{Enzo}\footnote{http://www.enzo-project.org} to simulate the chemodyanamical evolution and detailed feedback physics in a set of high resolution, isolated, low mass dwarf galaxies. \texttt{Enzo} is an open-source code that is undergoing continual, active development by many researchers across several institutions. We use a substantially modified version of the current development version of \texttt{Enzo} (version 2.X) in this work.\footnote{This version is contained in a publicly available fork of the main repository: https://bitbucket.org/aemerick/enzo-emerick. Specifically, simulations presented here were conducted at changeset 445de816fd99.} We solve the equations of hydrodynamics using a direct-Eulerian piecewise parabolic method \citep{ColellaWoodward1984, Bryan1995} and a two-shock approximate Riemann solver with progressive fallback to more diffusive Riemann solvers in the event that higher order methods produce negative densities or energies. We compute the total gravitational potential from gas self-gravity, stars, and a static background dark matter potential (see Section~\ref{sec:IC}. Self-gravity is computed with a multigrid Poisson solver. The collisionless star particles are evolved with an adaptive particle-mesh N-body solver at an effective force resolution of $\sim 2 \Delta x$, where $\Delta x$ is the local cell size.

The computational domain in an AMR simulation is adaptively refined up to a designated resolution limit for a given set of refinement criteria. We require that the Jeans length be resolved by a minimum of 8 cells, continually refining a given region until this criteria is met or the region reaches the maximum resolution. Our maximum resolution in the simulations presented here is 1.8 pc. At maximum resolution, the Jeans length can become under resolved, leading to artificial numerical fragmentation. Studies have shown that resolving the Jeans length by at least 4 cells is required to suppress this fragmentation \citep{Truelove1997}.

We set the star formation density threshold to the value at which the Jeans length becomes resolved by only 4 cells in sub-200 K gas, or about 200 \ccunit (as discussed further in Section~\ref{sec:star formation}). Forming stars from this gas will reduce the local density, ensuring the Jeans length is resolved. However, since star formation is not instantaneous, we employ a pressure floor to support gas against artificial collapse once its Jeans length becomes unresolved. This prevents dense, self-gravitating gas from rapidly reaching densities significantly above our resolution limit. The use of a pressure floor is common in galaxy scale simulations with limited dynamic range. %(\textbf{I contrasted this to Hu's work which allows arbitrarily high densities, hoping feedback mitigates how high the densities actually get, but took it out. Leave it in?})

@@

As part of the \texttt{Grackle} package, metal line cooling is modeled using pre-computed \texttt{Cloudy} \citep{Cloudy2013} \footnote{http://www.nublado.org/} tables interpolated as a function of density, temperature, and redshift, using the \citet{HM2012} UV metagalactic background. As discussed in more detail in Section~\ref{sec:diffusive heating}, we account for approximate self-shielding of H and He against this UV background. Using this prescription with metal line cooling tables computed under an optically thin assumption can lead to an order of magnitude overestimation of the cooling rate at certain densities. To address this issue, we use re-computed metal line tables consistent with the self-shielding approximation.  We have made these new tables public in the main \texttt{Grackle} repository. These are both discussed in greater detail in Appendix ~\ref{appendix:cooling}.

\subsection{Star Formation Algorithm}
\label{sec:star formation}
In order to resolve individual star formation events on galaxy scales, we implement a stochastic star formation algorithm adopted from \citet{Goldbaum2015,Goldbaum2016}. Each cell at the maximum refinement level is capable of forming stars if it meets the following local criteria: 1) $n_{\rm cell} > n_{\rm thresh}$, 2) $T_{\rm gas} < T_{\rm thresh}$, 3) $M_{\rm gas} > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local Jeans mass. Our fiducial values for $n_{\rm thresh}$ and $T_{\rm thresh}$ are 200~cm$^{-3}$ and 200~K respectively \textbf{justify choices}. We limit the fraction of a cell's gas mass that is converted into stars by requiring $M_{\rm gas} > f_{\rm thresh} M_{\rm max,*}$, where $f_{\rm thresh} = 2.0 $ and $M_{\rm max,*}$ is the maximum star mass (100 M$_{\odot}$). No star formation occurs when $M_{\rm gas} < f_{\rm thresh} M_{\rm max,*}$, ensuring that a star formation episode does not produce negative densities.

We make the common ansatz that star formation occurs by converting some fraction of gas into stars in a free fall time ($\tau_{\rm ff}$) as characterized by a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$. At high resolution, one's choice of $\epsilon_{\rm f}$ should be irrelevant \citep{Orr2017, FIRE2}, as star formation is ultimately self-regulated by feedback.
%but we find that $\epsilon_{\rm f}$ may impact star formation in the lowest mass halos, which are unusually sensitive to stellar ionization feedback (see Emerick et. al. in prep).
The gas mass converted to stars in a time step, $dt$, is
\begin{equation}
M_{ {\rm gas} \to *} = \epsilon_{\rm f} M_{\rm gas} \frac{dt}{\tau_{\rm ff}}.
\end{equation}
In practice, $dt/\tau_{\rm ff} \ll 1$, and $M_{ {\rm gas} \to *}$ is smaller than the minimum star particle mass at parsec scale resolution. We therefore allow star formation to proceed stochastically, following the methods in \citet{Goldbaum2015, Goldbaum2016}, modified for variable stellar masses. In each cell that could potentially form stars, we compute the probability that 100 M$_{\odot}$ of gas will be converted into stars in that time step, and use a random number draw to determine whether or not star formation actually occurs. If it does, we randomly sample over the adopted IMF until 100 M$_{\odot}$ of stars form, keeping the last sampled particle if the total stellar mass formed exceeds 100 M$_{\odot}$. We make the simple assumption of a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over a minimum stellar mass of 1 M$_{\odot}$ and maximum stellar mass of 100 M$_{\odot}$. Our lower limit on stellar masses ensures that we are able to both directly track all particles that participate in some way to feedback and metal enrichment, and follow longer lived start particles, while reducing the computational expense of following many low mass stars that have no dynamical impact on the galaxy evolution. 100 M$_{\odot}$ is a reasonable upper limit on the most massive star \textbf{sounds weak}.

Formed stars are deposited with random positions within the star forming cell and assigned velocities equal to the cell bulk velocity with a \textbf{1~km~s$^{-1}$ velocity dispersion - justify!}. Stars are assigned metallicities corresponding to the metallicity of the star forming zone, and are chemically tagged with the 17 individual species abundances (H, He, and the 15 metals) that we follow in our simulations. Stars evolve during the simulation, by losing mass from stellar winds and supernovae as described below, and by changing types, but persist throughout the entire simulation. For example, low mass stars are tagged as white dwarfs at the end of their life, which may eventually explode as a Type Ia supernova (discussed below), after which they persist as massless tracer particle ``remnants''.

@@

Above some mass $M_{\rm trans}$ within the unsampled range of 7--12 M$_{\odot}$, stars do not undergo AGB wind phases and end their lives as core collapse supernovae. Where this transition occurs is uncertain, but is commonly taken to be around 8--10~M$_{\odot}$. This is a free parameter in our model, but we take $M_{\rm trans} = 8$~M$_{\odot}$ as our fiducial value. In our model, stars below this mass eject their wind yields in an AGB phase only at the end of their lives, typically over a period comparable to or less than a few time steps ($\lesssim 10$ kyr). Stars above this mass are assumed to eject their stellar yields via line-driven stellar winds at a constant mass loss rate throughout their lifetime (neglecting Wolf-Rayet and luminous blue variable phases), ending their lives as a core-collapse supernova (see Section \ref{sec:stellar winds} for details on the wind energetics). Varying $M_{\rm thresh}$ changes both the time at which yields for stars around this mass are ejected (for reference, the lifetime of a 8 M$_{\odot}$ star is about 35--40~Myr), and the energy injection from these winds. \citet{Cote2017} explores how the choice of $M_{\rm thresh}$ affects galaxy abundances in a one-zone model.

@@

\subsubsection{Type Ia Supernova}
\label{sec:Type Ia}
We continue to track low mass stars ($M < 8$ M$_{\odot}$) after their death as white dwarf (WD) particles, marking a subset as Type Ia supernova progenitors. This is the most self-consistent model for Type 1a supernovae in galaxy scale simulations. \textbf{(Is this worth mentioning like this? or too strong a statement?)} We note however that for the low SFR's in our isolated dwarf galaxy simulations, the first SNIa only appears after a few hundred Myr of simulation time. For example, by the end of the simulation presented here (500~Myr), only 18 have gone off. At the end of their life, we assign a new mass to these particles following the initial-to-final-mass relation of \citet{Salaris2009}.
%mm \textbf{I originally reproduced the equations here, but it is currently commented out. - AE}
%or, 
%\[
%M_{\rm WD} = 
%\begin{cases}
%0.134 M_{\rm i} + 0.331 & 1.7~{\rm M_{\odot}} \le M_{\rm *} \le 4~{\rm M_{\odot}} \\
%0.047 M_{\rm i} + 0.679 & 4~{\rm M_{\odot}} \le M_{\rm *}
%\end{cases}
%\]
%where $M_{\rm *}$ is the initial mass of the WD progenitor.
We follow the common assumption that progenitor stars with masses between 3 and 8 M$_{\odot}$ form WD's that are Type Ia progenitors \citep[see][ and references therein]{Cote2017}.

We compute the probability that a given Type Ia progenitor will explode as a function of time using an observationally motivated delay time distribution (DTD) model. 
%\textbf{I went in detail on the DTD model here out of frustration of the lack of detail in other works, but I can trim this if needed (AE):} 
The SNIa rate is taken as a power law in time, $\Psi (t) \propto t^{-\beta}$, whose slope ($\beta$) and normalization ($N_{\rm 1a}/M_{\rm SF}$) are observables. The latter represents the number of Type 1a supernova per mass of star formation. By assuming an IMF, one can write down the fraction ($\eta$) of stars capable of forming a SNIa progenitor that \textit{will} explode within a Hubble time. This is given as
\begin{equation}
\eta = \frac{N_{\rm Ia}}{M_{\rm SF}} \frac{\int_{M_{\rm min}}^{M_{\rm max}} m (dN/dm) dm }{\int_{M_{1}}^{M_{2}} (dN/dm) dm},
\end{equation}
where $M_{\rm min}$ and $M_{\rm max}$ are the lower and upper bounds of the IMF ($dN/dm$), and $M_{1}$ and $M_{2}$ are the lower and upper bounds of the range of stars that can form Type Ia candidates. The DTD slope, $\beta$, is of order unity, with typical values between 1.0 and 1.2 (see \citet{Maoz2014} for a recent review). $N_{\rm Ia}/M_{\rm SF}$ can be derived by taking observed values of the SNIa rate and integrating over a Hubble time. Typical values for this are on order of 10$^{-3}$ M$_{\odot}^{-1}$ \citep{Maoz2014}. We adopt 1.2 \citep{Maoz2010} and 0.8$\times 10^{-3}$ M$_{\odot}^{-1}$ \citep{GraurMaoz2013} for our fiducial values of $\beta$ and $N_{\rm Ia}/M_{\rm SF}$. Given our choice of IMF, and with $M_{\rm min} = 1$~M$_{\odot}$, $M_{\rm max}=100$~M$_{\odot}$, $M_{1}=3$~M$_{\odot}$, and $M_{2}=8$~M$_{\odot}$, this gives $\eta = 0.041$.

@@

We also include the effects of radiation pressure on \ion{H}{1}. This has been shown to be important in suppressing the star formation rates of dwarf galaxies by influencing turbulence and the dense gas content of the ISM \citep{WiseAbel2012,Ceverino2014}. We ignore the absorption of ionizing radiation by dust and re-radiation in the infrared. This is included in other models \citep[e.g.][]{Rosdahl2015,FIRE,FIRE2} as this may increase by a factor of a few to several the effective radiation pressure \citep{ZhangDavis2017}. However, the importance of multiple scattering is still unclear. Other works have shown the effect to only increase the radiation pressure by a factor of order unity \citep{Krumholz2012,Krumholz2013,Reissl2017}. Due to these uncertainties, and given that our dwarf galaxy has a low dust content (and therefore a low IR opacity), we ignore this effect. \textbf{Greg referenced Dong Zheng in comments but I could not find anything for this}

\subsubsection{Diffuse  Heating}
\label{sec:diffusive heating}
We include two forms of diffuse heating in our simulations, each tied directly to the non-equilibrium primordial chemistry network in \texttt{Grackle}: 1) the optically thin, metagalactic UV background \citep{HM2012}, and 2) localized photoelectric heating from the far-ultraviolet (FUV, 6 eV $<$ $h\nu$ $<$ 13.6 eV) radiation from our stars. Photoelectric heating can be a dominant heating mechanism in the ISM of the Milky Way \citep{Parravano2003}, and could be significant in regulating star formation in dwarf galaxies \citep{Forbes2016}. However, this conclusion warrants further research as its exact importance in dwarf galaxies relative to other feedback mechanisms is contentious \citep{Hu2016,Hu2017}. Generally, models for photoelectric heating and Lyman-Werner radiation in hydrodynamic simulations of galaxies adopt a constant value or a static, radial profile. Only recently has the localization and time variation of these processes been considered.

@@

Our analysis makes extensive use of the open-source \textsc{yt} toolkit \citep{yt}. All analysis scripts used in this work can be found at https://github.com/aemerick/galaxy-analysis at changeset \textbf{changeset number}.

@@

We present the star formation rate (SFR) and core collapse supernova rate evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Figure~\ref{fig:sfr_mass_evolution}.\footnote{We do not show the Type 1a rate as there have only been 18 by the end of the simulation.} Within the first 40 Myr of evolution the SFR rises quickly to between $2--4 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, remains roughly this level for 100 Myr, and drops to an average of about $4 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, with large fluctuations. By the end of the simulation, the SFR is very low and infrequent, with an average SFR over the final 200~Myr of 2.58$\times 10^{-5}$~M$_{\odot}$~yr$^{-1}$. The SNR tracks the SFR with a time delay, with roughly one core collapse supernovae per 100 M$_{\odot}$ of star formation. Averaging over the entire simulation time, we obtain  $<\rm{SFR}> = 9.93 \times 10^{-5}$ M$_{\odot}$ yr$^{-1}$. We discuss how the SFR of this galaxy compares to observed galaxies in Section~\ref{sec:observation}.

@@

\begin{figure*}
\centering
\includegraphics[width=0.475\linewidth]{sfr_snr}
\includegraphics[width=0.475\linewidth]{mass_evolution}
\caption{Left: The SFR and core collapse supernova rate in our dwarf galaxy in 10 Myr bins (left). Right: The evolution of the total gas mass (black), \ion{H}{1} mass (blue), H$_2$ mass (orange), and stellar mass (red) in the disk of our galaxy over time. Note that the vertical axis limits in the left panel have been scaled to the same numerical values, yet with different units for the SFR and supernova rate.}
% This figure only includes gas present within the disk of the galaxy, as defined in the beginning of ~\Section{sec:results}.
\label{fig:sfr_mass_evolution}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.32\linewidth]{number_density} 
\includegraphics[width=0.32\linewidth]{temperature}\\
\includegraphics[width=0.32\linewidth]{log_OH} 
\includegraphics[width=0.32\linewidth]{log_NH}
\includegraphics[width=0.32\linewidth]{log_NO}
\caption{Five slices in the mid-place of our dwarf galaxy at an arbitrary time (XXX Myr) demonstrating the power of our chemical evolution model. We show the number density and temperature in this region of the galaxy (top row), along with three different elemental abundance ratios, O/H (bottom left), N/H (bottom middle), and N/O (bottom right). We caution against making direct comparisons of these images to observed abundances of dwarf galaxies, as we do not capture a cosmologically realistic chemical evolution in these relatively short ($< 1$~Gyr) simulations. This will be addressed in future work. \textbf{I need to adjust axis label size}}
\label{fig:metal_slices}
\end{figure*}

@@

\appendix

>>>>

\begin{abstract}
We have developed a new model for stellar feedback in order to simulate the chemodynamical evolution of isolated dwarf galaxies at high resolution in the adaptive mesh refinement hydrodynamics code \textsc{Enzo}. For the first time in galaxy scale simulations, we are capable of capturing detailed stellar feedback from individual stars including stellar winds from massive stars and AGB stars, photoelectric heating, Lyman-Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae. 
%This star-by-star method allows us to directly account for variations in stellar properties that govern their feedback properties (mass, lifetime, surface temperature, and metallicity).
In addition, we follow the evolution of star-by-star stellar yields for 15 metal tracer species: C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, St, Y, and Ba. We describe these methods in detail, including the additional physics used to model a realistic three-phase interstellar medium. We present the first application of these methods on a 500~Myr simulation of an isolated dwarf galaxy with properties similar to a Local Group ultrafaint dwarf galaxy. We demonstrate that our physics and feedback model is capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship. Effective feedback drives significant metal enriched outflows, leading to a low metal retention fractions consistent with observations. Our low-dust content galaxy exhibits a significant H$_2$ mass fraction, formed primarily through gas-phase H$^{-}$ reactions. We end with a discussion on how this work will impact our understanding of galactic chemical evolution on a species-by-species basis.
\end{abstract}

@@

We use the adaptive mesh refinement (AMR) hydrodynamics and N-body code \texttt{Enzo}\footnote{http://www.enzo-project.org} to simulate the chemodyanamical evolution and detailed feedback physics in a set of high resolution, isolated, low mass dwarf galaxies. \texttt{Enzo} is an open-source code that is undergoing continual, active development by many researchers across several institutions. We use a substantially modified version of the current development version of \texttt{Enzo} (version 2.X) in this work.\footnote{This version is contained in a publicly available fork of the main repository: https://bitbucket.org/aemerick/enzo-emerick. Specifically, simulations presented here were conducted at changeset 445de816fd99.} We solve the equations of hydrodynamics using a direct-Eulerian piecewise parabolic method \citep{ColellaWoodward1984, Bryan1995} and a two-shock approximate Riemann solver with progressive fallback to more diffusive Riemann solvers in the event that higher order methods produce negative densities or energies. We compute the total gravitational potential from gas self-gravity, stars, and a static background dark matter potential (see Section~\ref{sec:IC}). Self-gravity is computed with a multigrid Poisson solver. The collisionless star particles are evolved with an adaptive particle-mesh N-body solver at an effective force resolution of $\sim 2 \Delta x$, where $\Delta x$ is the local cell size.

The computational domain in an AMR simulation is adaptively refined up to a designated resolution limit for a given set of refinement criteria. We require that the Jeans length be resolved by a minimum of 8 cells, continually refining a given region until this criteria is met or the region reaches the maximum resolution. Our maximum resolution in the simulations presented here is 1.8~pc. At maximum resolution, the Jeans length can become under resolved, leading to artificial numerical fragmentation. Studies have shown that resolving the Jeans length by at least 4 cells is required to suppress this fragmentation \citep{Truelove1997}.

We set the star formation density threshold to the value at which the Jeans length becomes resolved by only 4 cells in sub-200 K gas, or about 200 \ccunit (as discussed further in Section~\ref{sec:star formation}). Forming stars from this gas will reduce the local density, ensuring the Jeans length is resolved. However, since star formation is not instantaneous, we employ a pressure floor to support gas against artificial collapse once its Jeans length becomes unresolved. This prevents dense, self-gravitating gas from rapidly reaching densities significantly above our resolution limit. The use of a pressure floor is common in galaxy scale simulations with limited dynamic range \citep[e.g][]{Machacek2001, RobertsonKravtsov2008}.

%(\textbf{I contrasted this to Hu's work which allows arbitrarily high densities, hoping feedback mitigates how high the densities actually get, but took it out. Leave it in?})

@@

As part of the \texttt{Grackle} package, metal line cooling is modeled using pre-computed \texttt{Cloudy} \citep{Cloudy2013} \footnote{http://www.nublado.org/} tables interpolated as a function of density, temperature, and redshift, using the \citet{HM2012} UV metagalactic background. As discussed in more detail in Section~\ref{sec:diffusive heating}, we account for approximate self-shielding of H and He against this UV background. Using this prescription with metal line cooling tables computed under an optically thin assumption can lead to an order of magnitude overestimation of the cooling rate at certain densities, as discussed in \citet{Hu2017} and  Appendix~\ref{appendix:cooling}. To address this issue, we use re-computed metal line tables consistent with the self-shielding approximation.  We have made these new tables public in the main \texttt{Grackle} repository. These are discussed in greater detail in Appendix ~\ref{appendix:cooling}.

\subsection{Star Formation Algorithm}
\label{sec:star formation}
In order to resolve individual star formation events on galaxy scales, we implement a stochastic star formation algorithm adopted from \citet{Goldbaum2015,Goldbaum2016}. Each cell at the maximum refinement level is capable of forming stars if it meets the following local criteria: 1) $n_{\rm cell} > n_{\rm thresh}$, 2) $T_{\rm gas} < T_{\rm thresh}$, 3) $M_{\rm gas} > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local Jeans mass. Our fiducial values for $n_{\rm thresh}$ and $T_{\rm thresh}$ are 200~cm$^{-3}$ and 200~K respectively. We limit the fraction of a cell's gas mass that is converted into stars by requiring $M_{\rm gas} > f_{\rm thresh} M_{\rm max,*}$, where $f_{\rm thresh} = 2.0 $ and $M_{\rm max,*}$ is the maximum star mass (100 M$_{\odot}$). No star formation occurs when $M_{\rm gas} < f_{\rm thresh} M_{\rm max,*}$, ensuring that a star formation episode does not produce negative densities.

We make the common ansatz that star formation occurs by converting some fraction of gas into stars in a free fall time ($\tau_{\rm ff}$) as characterized by a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$. At high resolution, one's choice of $\epsilon_{\rm f}$ should be irrelevant \citep{Orr2017, FIRE2}, as star formation is ultimately self-regulated by feedback.
%but we find that $\epsilon_{\rm f}$ may impact star formation in the lowest mass halos, which are unusually sensitive to stellar ionization feedback (see Emerick et. al. in prep).
The gas mass converted to stars in a time step, $dt$, is
\begin{equation}
M_{ {\rm gas} \to *} = \epsilon_{\rm f} M_{\rm gas} \frac{dt}{\tau_{\rm ff}}.
\end{equation}
In practice, $dt/\tau_{\rm ff} \ll 1$, and $M_{ {\rm gas} \to *}$ is smaller than the minimum star particle mass at parsec scale resolution. We therefore allow star formation to proceed stochastically, following the methods in \citet{Goldbaum2015, Goldbaum2016}, modified for variable stellar masses. In each cell that could potentially form stars, we compute the probability that 100 M$_{\odot}$ of gas will be converted into stars in that time step, and use a random number draw to determine whether or not star formation actually occurs. If it does, we randomly sample over the adopted IMF until 100 M$_{\odot}$ of stars form, keeping the last sampled particle if the total stellar mass formed exceeds 100 M$_{\odot}$. We make the simple assumption of a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over a minimum stellar mass of 1 M$_{\odot}$ and an arbitrarily chosen maximum stellar mass of 100 M$_{\odot}$. Our lower limit on stellar masses ensures that we are able to both directly track all particles that participate in some way to feedback and metal enrichment, and follow longer lived start particles, while reducing the computational expense of following many low mass stars that have no dynamical impact on the galaxy evolution.

Formed stars are deposited with random positions within the star forming cell and assigned velocities equal to the cell bulk velocity with a 1~km~s$^{-1}$ velocity dispersion. This dispersion captures some of the unresolved gas motions below the resolution limit and smoothed out by numerical diffusion; it is comparable to, but less than, the velocity dispersion of the coldest gas in our simulations. Stars are assigned metallicities corresponding to the metallicity of the star forming zone, and are chemically tagged with the 17 individual species abundances (H, He, and the 15 metals) that we follow in our simulations. Stars evolve during the simulation, by losing mass from stellar winds and supernovae as described below, and by changing types, but persist throughout the entire simulation. For example, low mass stars are tagged as white dwarfs at the end of their life, which may eventually explode as a Type Ia supernova (discussed below), after which they persist as massless tracer particle ``remnants''.

@@

Above some mass $M_{\rm trans}$ within the unsampled range of 7--12 M$_{\odot}$, stars do not undergo AGB wind phases and end their lives as core collapse supernovae. Where this transition occurs is uncertain, but is commonly taken to be around 8--10~M$_{\odot}$. This is a free parameter in our model, but we take $M_{\rm trans} = 8$~M$_{\odot}$ as our fiducial value. In our model, stars below this mass eject their wind yields in an AGB phase only at the end of their lives, typically over a period comparable to or less than a few time steps ($\lesssim 10$ kyr). Stars above this mass are assumed to eject their stellar yields via line-driven stellar winds at a constant mass loss rate throughout their lifetime (neglecting Wolf-Rayet and luminous blue variable phases), ending their lives as a core-collapse supernova (see Section \ref{sec:stellar winds} for details on the wind energetics). Varying $M_{\rm thresh}$ changes both the time at which yields for stars around this mass are ejected (for reference, the lifetime of a 8 M$_{\odot}$ star is about 35--40~Myr), and the energy injection from these winds. \citet{Cote2017} explores how the choice of $M_{\rm thresh}$ affects galaxy abundances in a one-zone model. We neglect the effects of binary star evolution on stellar feedback, but discuss the significance of this in Section~\ref{sec:binary stars}.

@@

\subsubsection{Type Ia Supernova}
\label{sec:Type Ia}
We continue to track low mass stars ($M < 8$ M$_{\odot}$) after their death as white dwarf (WD) particles, marking a subset as Type Ia supernova progenitors. This is the most self-consistent model for Type Ia supernovae in galaxy scale simulations. We note however that for the low SFR's in our isolated dwarf galaxy simulations, the first SNIa only appears after a few hundred Myr of simulation time. For example, by the end of the simulation presented here (500~Myr), only 18 have gone off. At the end of their life, we assign a new mass to these particles following the initial-to-final-mass relation of \citet{Salaris2009}.
%mm \textbf{I originally reproduced the equations here, but it is currently commented out. - AE}
%or, 
%\[
%M_{\rm WD} = 
%\begin{cases}
%0.134 M_{\rm i} + 0.331 & 1.7~{\rm M_{\odot}} \le M_{\rm *} \le 4~{\rm M_{\odot}} \\
%0.047 M_{\rm i} + 0.679 & 4~{\rm M_{\odot}} \le M_{\rm *}
%\end{cases}
%\]
%where $M_{\rm *}$ is the initial mass of the WD progenitor.
We follow the common assumption that progenitor stars with masses between 3 and 8 M$_{\odot}$ form WD's that are Type Ia progenitors \citep[see][ and references therein]{Cote2017}.

We compute the probability that a given Type Ia progenitor will explode as a function of time using an observationally motivated delay time distribution (DTD) model. 
%\textbf{I went in detail on the DTD model here out of frustration of the lack of detail in other works, but I can trim this if needed (AE):} 
The SNIa rate is taken as a power law in time, $\Psi (t) \propto t^{-\beta}$, whose slope ($\beta$) and normalization ($N_{\rm Ia}/M_{\rm SF}$) are observables. The latter represents the number of Type Ia supernova per mass of star formation. By assuming an IMF, one can write down the fraction ($\eta$) of stars capable of forming a SNIa progenitor that \textit{will} explode within a Hubble time. This is given as
\begin{equation}
\eta = \frac{N_{\rm Ia}}{M_{\rm SF}} \frac{\int_{M_{\rm min}}^{M_{\rm max}} m (dN/dm) dm }{\int_{M_{1}}^{M_{2}} (dN/dm) dm},
\end{equation}
where $M_{\rm min}$ and $M_{\rm max}$ are the lower and upper bounds of the IMF ($dN/dm$), and $M_{1}$ and $M_{2}$ are the lower and upper bounds of the range of stars that can form Type Ia candidates. The DTD slope, $\beta$, is of order unity, with typical values between 1.0 and 1.2 (see \citet{Maoz2014} for a recent review). $N_{\rm Ia}/M_{\rm SF}$ can be derived by taking observed values of the SNIa rate and integrating over a Hubble time. Typical values for this are on order of 10$^{-3}$ M$_{\odot}^{-1}$ \citep{Maoz2014}. We adopt 1.2 \citep{Maoz2010} and 0.8$\times 10^{-3}$ M$_{\odot}^{-1}$ \citep{GraurMaoz2013} for our fiducial values of $\beta$ and $N_{\rm Ia}/M_{\rm SF}$. Given our choice of IMF, and with $M_{\rm min} = 1$~M$_{\odot}$, $M_{\rm max}=100$~M$_{\odot}$, $M_{1}=3$~M$_{\odot}$, and $M_{2}=8$~M$_{\odot}$, this gives $\eta = 0.041$.

@@

We also include the effects of radiation pressure on \ion{H}{1}. This has been shown to be important in suppressing the star formation rates of dwarf galaxies by influencing turbulence and the dense gas content of the ISM \citep{WiseAbel2012,Ceverino2014}. We ignore the absorption of ionizing radiation by dust and re-radiation in the infrared. This is included in other models \citep[e.g.][]{Rosdahl2015,FIRE,FIRE2} as this may increase by a factor of a few to several the effective radiation pressure \citep{ZhangDavis2017}. However, the importance of multiple scattering is still unclear. Other works have shown the effect to only increase the radiation pressure by a factor of order unity \citep{Krumholz2012,Krumholz2013,Reissl2017}. Due to these uncertainties, and given that our dwarf galaxy has a low dust content (and therefore a low IR opacity), we ignore this effect. \textbf{cite davis and stone, Zhang and davis?}

\subsubsection{Diffuse  Heating}
\label{sec:diffusive heating}
We include two forms of diffuse heating in our simulations, each tied directly to the non-equilibrium primordial chemistry network in \texttt{Grackle}: 1) the optically thin, uniform metagalactic UV background \citep{HM2012}, and 2) localized photoelectric heating from the far-ultraviolet (FUV, 6 eV $<$ $h\nu$ $<$ 13.6 eV) radiation from each of our star particles. Photoelectric heating can be a dominant heating mechanism in the ISM of the Milky Way \citep{Parravano2003}, and could be significant in regulating star formation in dwarf galaxies \citep{Forbes2016}. However, this conclusion warrants further research as its exact importance in dwarf galaxies relative to other feedback mechanisms is contentious \citep{Hu2016,Hu2017}. Generally, models for photoelectric heating and Lyman-Werner radiation in hydrodynamic simulations of galaxies adopt a constant value or a static, radial profile. Only recently has the localization and time variation of these processes been considered.

@@

Our analysis makes extensive use of the open-source \textsc{yt} toolkit \citep{yt}. All analysis scripts used in this work can be found at https://github.com/aemerick/galaxy-analysis at changeset 66452ba.

@@

We present the star formation rate (SFR) and core collapse supernova rate evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Figure~\ref{fig:sfr_mass_evolution}.\footnote{We do not show the Type Ia rate as there have only been 18 by the end of the simulation.} Within the first 40 Myr of evolution the SFR rises quickly to between $2---4 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, remains roughly this level for 100 Myr, and drops to an average of about $4 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, with large fluctuations. By the end of the simulation, the SFR is very low and infrequent, with an average SFR over the final 200~Myr of 2.58$\times 10^{-5}$~M$_{\odot}$~yr$^{-1}$. The SNR tracks the SFR with a time delay, with roughly one core collapse supernovae per 100 M$_{\odot}$ of star formation. Averaging over the entire simulation time, we obtain  $<\rm{SFR}> = 9.93 \times 10^{-5}$ M$_{\odot}$ yr$^{-1}$. We discuss how the SFR of this galaxy compares to observed galaxies in Section~\ref{sec:observation}.

@@

\begin{figure*}
\centering
\includegraphics[width=0.475\linewidth]{sfr_snrx100}
\includegraphics[width=0.475\linewidth]{mass_evolution}
\caption{Left: The SFR and core collapse supernova rate in our dwarf galaxy in 10 Myr bins (left). Right: The evolution of the total gas mass (black), \ion{H}{1} mass (blue), H$_2$ mass (orange), and stellar mass (red) in the disk of our galaxy over time. Note that the vertical axis limits in the left panel have been scaled to the same numerical values, yet with different units for the SFR and supernova rate.}
% This figure only includes gas present within the disk of the galaxy, as defined in the beginning of ~\Section{sec:results}.
\label{fig:sfr_mass_evolution}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.32\linewidth]{number_density} 
\includegraphics[width=0.32\linewidth]{temperature}\\
\includegraphics[width=0.32\linewidth]{log_OH} 
\includegraphics[width=0.32\linewidth]{log_NH}
\includegraphics[width=0.32\linewidth]{log_NO}
\caption{Five slices in the mid-place of our dwarf galaxy at an arbitrary time demonstrating the power of our chemical evolution model. We show the number density and temperature in this region of the galaxy (top row), along with three different elemental abundance ratios, O/H (bottom left), N/H (bottom middle), and N/O (bottom right). We caution against making direct comparisons of these images to observed abundances of dwarf galaxies, as we do not capture a cosmologically realistic chemical evolution in these relatively short ($< 1$~Gyr) simulations. This will be addressed in future work. \textbf{(AE: need to adjust axis label size)}}
\label{fig:metal_slices}
\end{figure*}

@@

\appendix
\renewcommand\thefigure{\thesection.\arabic{figure}}    
\setcounter{figure}{0}
